## Neural Nets
eyes - student has their eyes open (1 = yes, 0 = no)
face.forward - student is facing the camera (1 = yes, 0 = no)
chin.up - student's chin is raised above 45 degrees (1 = yes, 0 = no)
attention - whether the student was paying attention when asked (1 = yes, 0 = no)

# First Install and Load the neuralnet Package
```{r}
install.packages("neuralnet")
library(neuralnet)
```

# Now upload your data
```{r}
D1 <- read.csv("attention1.csv")
  
D2 <- read.csv("attention2.csv")
```

# Building a Neural Net
```{r}
net <- neuralnet(attention ~ eyes + face.forward + chin.up, D1, hidden = 1, threshold = 0.01)

plot(net)
```
```{r}
net2 <- neuralnet(attention ~ eyes + face.forward + chin.up, D1, hidden = 5, threshold=0.01)
plot(net2)
```

# Predict the second data set.
```{r}
D3 <- D2[,-4]
```

# Create predictions using your neural net
```{r}

net.prediction <- neuralnet::compute(net, D3)
pred1<-ifelse(net.prediction$net.result < 0.5, 0, 1)
table(pred1, D2$attention)

# Second neural network with 5 hidden layers
net.prediction2 <- neuralnet::compute(net2, D3)
pred2<-ifelse(net.prediction2$net.result < 0.5, 0, 1)
table(pred2, D2$attention)

#Both prediction accuracy remains the same regardless of the amount of layers. 
```